\cvsection{Projects}
\begin{cventries}
  \cventry
    {Master Thesis Project}
    {Automated Prediction of Experimental Metadata from Scientific Publications (\href{https://github.com/stutinayak/Thesis_metadata_wizard}{Link})}
    {Maastricht, Netherlands} 
    {Sept. 2018 - Feb. 2019}
    {
      \begin{cvitems}
        \item {Used deep learning (CNN and BiLSTM) to predict metadata}
        \item {Comparison of performances of Machine Learning and Deep Learning, where CNN has the best performance}
        %\item {CNN outperforms all the techniques}
      \end{cvitems}
    }
  \cventry
    {Internship Project}
    {Quality Assessment of Biomedical Metadata using Machine Learning}
    {Maastricht, Netherlands}
    {March 2018 - July 2018}
    {
      \begin{cvitems}
        \item {Used Binary Classification on a gold-standard data to assess the biomedical metadata quality assessment}
        \item {Comparison between multi-class classification and binary classification, binary classification}
      \end{cvitems}
    }
  \cventry
    {Research Project}
    {Quality Assessment of Biomedical Metadata using Topic Modeling}
    {Maastricht, Netherlands}
    {July 2017 - Jan. 2018}
    {
      \begin{cvitems}
        \item {Used topic modeling to cluster similar metadata elements}
        \item {Used BioSamples dataset as a use case to check the feasibility}
      \end{cvitems}
    }
  \cventry
    {Masters Research Project}
    {Prediction of Atrial Fibrillation (AFib) Recurrence for patients undergoing Electro-Cardioversion}
    {Maastricht, Netherlands}
    {Sep. 2017 - Jan. 2018}
   {Developed a gradient boosting model to see which set of features help predicting the recurrence of AFib. The clinical features like age, height, BMI were found to be of high importance}
   
\cventry
    {Masters Research Project}
    {Discovery connectivity in brain}
    {Maastricht, Netherlands}
    {Feb. 2017 - Jun. 2017}
    {
       % \begin{cvitems}
        % \item {
         Developed a method to analyze detect non-linear spectral causality in multivariate system for understanding connectivity in brain 
        % }
       % \end{cvitems}
    }
    
  \cventry
    {B.Tech Project}
    {Query execution in column stores vis-à-vis row stores}
    {Gandhinagar, India}
    {Jan. 2016 - April 2016}
    {
      \begin{cvitems}
        \item {Literature survey of performance column stores when compared to row stores in read queries}
        \item {Comparison of results on various databases using TPC-H benchmark}
      \end{cvitems}
    }
\end{cventries}
